\papertitle

### 2021-03-12 source_separation/paper/paper.tex
Edits from reading through, add back future work paragraph and plot

	Computer-assisted orchestrations can be divided into two categories: static and dynamic. Static orchestration considers the target as a single vector of timbral features and creates a single onset of note(s) as the solution. Dynamic orchestration considers a time series of features, which allows it to create an orchestration that evolves over time with multiple onsets.

@@

	We test the effectiveness of five difference source separation methods, both supervised and unsupervised, on 300 custom made targets that are combinations of sounds from different databases. During testing, a target is input to a source separation method, which outputs four sub-targets. Then each sub-target is independently orchestrated with a randomly assigned subset of the full orchestra. These orchestrations are then combined to play simultaneously, creating a final orchestrated solution. Then the distance between the target and solution is calculated, giving us a metric to compare the various separation methods. The random split of the orchestra is the same for each separation method of the same target. See Figure \ref{fig:eval_diagram} for a diagram of this process.

@@

		The procedure we used for testing is as follows:
		\begin{enumerate}
			\item The target is created as a combination of four randomly chosen sources, which are offset to begin playing at different times
			\item The full target, without any separation performed, is orchestrated using the entire orchestra
			\item Each separation method is performed on the target, each splitting the target into four sub-targets 
			\item The full orchestra is randomly split into four equal sized subsets
			\item For each method, the four sub-targets are separately orchestrated, each using a different subset of the orchestra, and then each orchestration is combined to play simultaneously
			\item The ground truth orchestration is created by orchestrating the four sources, using the same orchestra splits from step 4, and then combined to play simultaneously
			\item The distances between target and orchestration are calculated for the full target orchestration, the separated orchestration, and the ground truth orchestration 
		\end{enumerate}

		\begin{figure}[t]
			\centering
				\includegraphics[width=\columnwidth]{figures/evaluation_diagram.png}
				\caption{Diagram showing the testing method. Note that in both orchestrations that use a split orchestra, the split is the same.}\label{fig:eval_diagram}
		\end{figure}

@@

		As described in Section \ref{subsec:data}, each target is comprised of four sources that are offset in time to begin playing at different times. Figure \ref{fig:orchestrations} illustrates the effect this offset has on the full target, separated, and ground truth orchestrations. The full target orchestration places all onsets at the beginning of the orchestration, since it is unable to differentiate between different sources, it cannot place the different orchestrations at the appropriate offsets. However, the separated orchestrations are able to correctly place the onsets of the sub-target orchestrations so far as the method has correctly separated out the sources. In the ground truth orchestration, the sources are offset by the same amount as they are in the creation of the target, leading to the ground truth having each source orchestration beginning at the correct time.

>>>>

	Computer-assisted orchestrations can be divided into two categories: static and dynamic. Static orchestration considers the target as a single vector of timbral features and creates a single onset of note(s) as the solution. Dynamic orchestration considers a time series of features, which allows it to create an orchestration that evolves over time with multiple onsets. It uses time segmentation to cut the target in time into multiple segments, and orchestrates each segment.

@@

	We test the effectiveness of five difference source separation methods, both supervised and unsupervised, on 300 custom made targets that are combinations of sounds from different databases. During testing, a target is input to a source separation method, which outputs four sub-targets. Then each sub-target is independently orchestrated with a randomly assigned subset of the full orchestra. These orchestrations are then combined to play simultaneously, creating a final orchestrated solution. Then the distance between the target and solution is calculated, giving us a metric to compare the various separation methods. The random split of the orchestra is the same for each separation method of the same target. See Fig. \ref{fig:eval_diagram} for a diagram of this process.

@@

		The procedure we use for testing is as follows:
		\begin{enumerate}
			\item The target is created as a combination of four randomly chosen sources, which are offset to begin playing at different times
			\item The full target, without any separation performed, is orchestrated using the entire orchestra
			\item Each separation method is performed on the target, each splitting the target into four sub-targets 
			\item The full orchestra is randomly split into four equal sized subsets
			\item For each method, the four sub-targets are separately orchestrated, each using a different subset of the orchestra, and then each orchestration is combined to play simultaneously
			\item The ground truth orchestration is created by orchestrating the four sources, using the same orchestra splits from step 4, and then combined to play simultaneously
			\item The distances between target and orchestration are calculated for the full target orchestration, the separated orchestration, and the ground truth orchestration 
		\end{enumerate}

		\begin{figure}[t]
			\centering
				\includegraphics[width=\columnwidth]{figures/evaluation_diagram.png}
				\caption{Diagram showing the testing process. Note that in both orchestrations that use a split orchestra, the split is the same.}\label{fig:eval_diagram}
		\end{figure}

@@

		As described in Section \ref{subsec:data}, each target is comprised of four sources that are offset in time to begin playing at different times. Figure \ref{fig:orchestrations} illustrates the effect this offset has on the full target, separated, and ground truth orchestrations. The full target orchestration places all onsets at the beginning of the orchestration, since it is unable to differentiate between different sources, it cannot place the different orchestrations at the appropriate offsets. However, the separated orchestrations are able to correctly place the onsets of the sub-target orchestrations so far as the method has correctly separated out the sources. In the ground truth orchestration, the sources are offset by the same amount as they are in the creation of the target, leading to the ground truth having each source orchestration beginning at the correct time. For this reason, despite only performing static orchestrations, the resulting separated and ground truth orchestrations are offset in time compared to the full target orchestration.
